---
title: "Item Selection - All Items"
author: "Mubashir Sultan"
date: "3/2/2021"
output: html_document
---


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r libraries and initial setup,  include=FALSE}
#loading libraries
library(readr)
library(readxl)
library(writexl)
library(tidyverse)
library(jtools)
```

```{r loading dataset,  include=FALSE}
rm(list=ls());

# reading excel sheet
df <- read_excel("/Users/mubashirsultan/Dropbox/partisanship selection example_RP2.xlsx", sheet = 1, col_names = TRUE, col_types = NULL)

# removing unnecessary columns
df_slim <- df[, c("Item #", "Category", "Image Name", "Headline Summary", "Acc_Abs_Dem", "Acc_Abs_Rep","Acc_Dem", "Acc_Rep", "Fam_Dem", "Fam_Rep", "Par_Combined")]

#add whether the items are democratic favoured or republican favoured
df_slim$Par_Combined <- ifelse(df_slim$Par_Combined > 3.5, "Rep Favoured", "Dem Favoured")

# long format
df_slim_long <- gather(df_slim, key = "measurement", value = "value", -c("Item #", "Category", "Image Name", "Headline Summary", "Par_Combined"))

# adding political variable
df_slim_long$political_leaning <- "Democrat"

df_slim_long$political_leaning <- ifelse(str_detect(df_slim_long$measurement, "Rep") == TRUE, df_slim_long$political_leaning <- "Republican", df_slim_long$political_leaning <- "Democrat")

df_slim_long$measurement <- str_replace(df_slim_long$measurement, c("_Rep"), "")
df_slim_long$measurement <- str_replace(df_slim_long$measurement, c("_Dem"), "")

#adding classes
df_slim_long$measurement <- factor(df_slim_long$measurement, levels = c("Acc_Abs", "Acc", "Fam"))
df_slim_long$Par_Combined <- factor(df_slim_long$Par_Combined, levels = c("Dem Favoured", "Rep Favoured"))

```


```{r creating political df,  include=FALSE}
df_political <- df_slim_long

#political true only
df_political_true <- df_slim_long %>% filter(Category == "Political_True" | Category == "COVID_True")

#political false only
df_political_false <- df_slim_long %>% filter(Category == "Political_Fake" | Category == "COVID_Fake")

# #political true only
# df_political_true <- df_slim_long %>% filter(Category == "Political_True")
# df_COVID_true <- df_slim_long %>% filter(Category == "COVID_True")
# 
# #political false only
# df_political_false <- df_slim_long %>% filter(Category == "Political_Fake")
# df_COVID_false <- df_slim_long %>% filter(Category == "COVID_Fake")
# 
# # adding a category relevant political lean
# df_political_true$Par_Combined_Break <- str_replace(df_political_true$Par_Combined, "Dem", "Political Dem")
# tmp <- str_detect(df_political_true$Par_Combined_Break, "Political Dem")
# df_political_true$Par_Combined_Break[!tmp] <- "Political Rep Favoured"
# 
# df_COVID_true$Par_Combined_Break <- str_replace(df_COVID_true$Par_Combined, "Dem", "COVID Dem")
# tmp <- str_detect(df_COVID_true$Par_Combined_Break, "COVID Dem")
# df_COVID_true$Par_Combined_Break[!tmp] <- "COVID Rep Favoured"
# 
# # adding a category relevant political lean
# df_political_false$Par_Combined_Break <- str_replace(df_political_false$Par_Combined, "Dem", "Political Dem")
# tmp <- str_detect(df_political_false$Par_Combined_Break, "Political Dem")
# df_political_false$Par_Combined_Break[!tmp] <- "Political Rep Favoured"
# 
# df_COVID_false$Par_Combined_Break <- str_replace(df_COVID_false$Par_Combined, "Dem", "COVID Dem")
# tmp <- str_detect(df_COVID_false$Par_Combined_Break, "COVID Dem")
# df_COVID_false$Par_Combined_Break[!tmp] <- "COVID Rep Favoured"

```

# Descriptives across the categories (Political_True and _False AND COVID_True and _False)
```{r descriptives across cateogires}
df_political %>% group_by(Category, measurement) %>%
  summarise(mean = mean(value), SD = sd(value), count = n(), se = (SD/(sqrt(count))), median = median(value), min = min(value), max = max(value))

# Basic histogram Absolute Accuracy
df_political %>% filter(measurement == "Acc_Abs") %>% ggplot(aes(x=value)) + geom_histogram() + theme_apa() + labs(title = "Accuracy Histogram - Percentage", x = "Percentage Values", y = "Count",  subtitle = "For all values collapsed across political leaning and items") + geom_vline(aes(xintercept = mean(value)), linetype="dashed") 

# Basic boxplot Absolute Accuracy
df_political %>% filter(measurement == "Acc_Abs") %>% ggplot(aes(x=value)) + geom_boxplot() + theme_apa() + labs(title = "Accuracy Boxplot - Percentage", x = "Percentage Values", y = "Count",  subtitle = "For all values collapsed across political leaning and items")

# Basic histogram Absolute Accuracy
df_political %>% filter(measurement == "Acc_Abs") %>% ggplot(aes(x=value)) + geom_histogram() + theme_apa() + labs(title = "Accuracy Histogram - Percentage", x = "Percentage Values", y = "Count", subtitle = "Grouped by all categories, collapsed acorss political leaning") + facet_wrap(~Category)

# Basic boxplot Absolute Accuracy
df_political %>% filter(measurement == "Acc_Abs") %>% ggplot(aes(x=value)) + geom_boxplot() + theme_apa() + labs(title = "Accuracy Boxplot - Percentage", x = "Percentage Values", y = "Count",  subtitle = "For all values collapsed across political leaning and items") + facet_wrap(~Category)


# Basic histogram Relative Accuracy
df_political %>% filter(measurement == "Acc") %>% ggplot(aes(x=value)) + geom_histogram() + theme_apa() + labs(title = "Accuracy Histogram - Likert means", x = "Likert Values", y = "Count",  subtitle = "For all values collapsed across political leaning and items \n 1: extremely unlikely; 6 extremely likely") + geom_vline(aes(xintercept = mean(value)), linetype="dashed") 

# Basic histogram Relative Accuracy
df_political %>% filter(measurement == "Acc") %>% ggplot(aes(x=value)) + geom_histogram() + theme_apa() + labs(title = "Accuracy Histogram - Likert means", x = "Likert Values", y = "Count", subtitle = "Collapsed acorss political leaning \n 1: extremely unlikely; 6 extremely likely") + facet_wrap(~Category)

# Basic histogram Familiarity 
df_political %>% filter(measurement == "Fam") %>% ggplot(aes(x=value)) + geom_histogram() + theme_apa() + labs(title = "Familiarity Histogram - Likert means", x = "Likert Values", y = "Count",  subtitle = "For all values collapsed across political leaning and items \n 1: not at all; 6 extremely") + geom_vline(aes(xintercept = mean(value)), linetype="dashed")

# Basic histogram Familiarity
df_political %>% filter(measurement == "Fam") %>% ggplot(aes(x=value)) + geom_histogram() + theme_apa() + labs(title = "Familiarity Histogram - Likert means", x = "Likert Values", y = "Count", subtitle = "Collapsed acorss political leaning \n 1: not at all; 6 extremely") + facet_wrap(~Category)

```


# Descriptives across the _True only
```{r descriptives Political True only}
df_political_true %>% group_by(Category, political_leaning, measurement) %>%
  summarise(mean = mean(value), SD = sd(value), count = n(), se = (SD/(sqrt(count))), median = median(value), min = min(value), max = max(value))

# Basic histogram Absolute Accuracy
df_political_true %>% filter(measurement == "Acc_Abs") %>% ggplot(aes(x=value, fill = Category)) + geom_histogram() + theme_apa() + labs(title = "Accuracy Histogram - Percentage", x = "Percentage Values", y = "Count", subtitle = "For _True only, collapsed across political leaning") + geom_vline(aes(xintercept = mean(value)), linetype="dashed") 

# Basic histogram Absolute Accuracy
df_political_true %>% filter(measurement == "Acc_Abs") %>% ggplot(aes(x=value, fill = Category)) + geom_histogram() + theme_apa() + labs(title = "Accuracy Histogram - Percentage", x = "Percentage Values", y = "Count", subtitle = "For _True only") + facet_wrap(~political_leaning)

# Basic histogram Relative Accuracy
df_political_true %>% filter(measurement == "Acc") %>% ggplot(aes(x=value, fill = Category)) + geom_histogram() + theme_apa() + labs(title = "Accuracy Histogram - Likert means", x = "Likert Values", y = "Count", subtitle = "For _True only, collapsed across political leaning \n 1: extremely unlikely; 6 extremely likely") + geom_vline(aes(xintercept = mean(value)), linetype="dashed") 

# Basic histogram Relative Accuracy
df_political_true %>% filter(measurement == "Acc") %>% ggplot(aes(x=value, fill = Category)) + geom_histogram() + theme_apa() + labs(title = "Accuracy Histogram - Likert means", x = "Likert Values", y = "Count", subtitle = "For _True only \n 1: extremely unlikely; 6 extremely likely") + facet_wrap(~political_leaning)

# Basic histogram Familiarity 
df_political_true %>% filter(measurement == "Fam") %>% ggplot(aes(x=value, fill = Category)) + geom_histogram() + theme_apa() + labs(title = "Familiarity Histogram - Likert means", x = "Likert Values", y = "Count", subtitle = "For _True only, collapsed across political leaning \n 1: not at all; 6 extremely") + geom_vline(aes(xintercept = mean(value)), linetype="dashed") 

# Basic histogram Familiarity
df_political_true %>% filter(measurement == "Fam") %>% ggplot(aes(x=value, fill = Category)) + geom_histogram() + theme_apa() + labs(title = "Familiarity Histogram - Likert means", x = "Likert Values", y = "Count", subtitle = "For _True only \n 1: not at all; 6 extremely") + facet_wrap(~political_leaning)

```


# Descriptives across the _False only
```{r descriptives Political False only}
df_political_false %>% group_by(Category, political_leaning, measurement) %>%
  summarise(mean = mean(value), SD = sd(value), count = n(), se = (SD/(sqrt(count))), median = median(value), min = min(value), max = max(value))

# Basic histogram Absolute Accuracy
df_political_false %>% filter(measurement == "Acc_Abs") %>% ggplot(aes(x=value, fill = Category)) + geom_histogram() + theme_apa() + labs(title = "Accuracy Histogram - Percentage", x = "Percentage Values", y = "Count", subtitle = "For _False only, collapsed across political leaning") + geom_vline(aes(xintercept = mean(value)), linetype="dashed")

# Basic histogram Absolute Accuracy
df_political_false %>% filter(measurement == "Acc_Abs") %>% ggplot(aes(x=value, fill = Category)) + geom_histogram() + theme_apa() + labs(title = "Accuracy Histogram - Percentage", x = "Percentage Values", y = "Count", subtitle = "For _False only") + facet_wrap(~political_leaning)

# Basic histogram Relative Accuracy
df_political_false %>% filter(measurement == "Acc") %>% ggplot(aes(x=value, fill = Category)) + geom_histogram() + theme_apa() + labs(title = "Accuracy Histogram - Likert means", x = "Likert Values", y = "Count", subtitle = "For _False only, collapsed across political leaning \n 1: extremely unlikely; 6 extremely likely") + geom_vline(aes(xintercept = mean(value)), linetype="dashed")

# Basic histogram Relative Accuracy
df_political_false %>% filter(measurement == "Acc") %>% ggplot(aes(x=value, fill = Category)) + geom_histogram() + theme_apa() + labs(title = "Accuracy Histogram - Likert means", x = "Likert Values", y = "Count", subtitle = "For _False only \n 1: extremely unlikely; 6 extremely likely") + facet_wrap(~political_leaning)

# Basic histogram Familiarity 
df_political_false %>% filter(measurement == "Fam") %>% ggplot(aes(x=value, fill = Category)) + geom_histogram() + theme_apa() + labs(title = "Familiarity Histogram - Likert means", x = "Likert Values", y = "Count", subtitle = "For _False only, collapsed across political leaning \n 1: not at all; 6 extremely") + geom_vline(aes(xintercept = mean(value)), linetype="dashed") 

# Basic histogram Familiarity
df_political_false %>% filter(measurement == "Fam") %>% ggplot(aes(x=value, fill = Category)) + geom_histogram() + theme_apa() + labs(title = "Familiarity Histogram - Likert means", x = "Likert Values", y = "Count", subtitle = "For _False only \n 1: not at all; 6 extremely") + facet_wrap(~political_leaning)

```


```{r creating political df with values 3SD on accuracy removed,  include=FALSE}
# identifying outliers for accuracy - in both the political true and political false data

#political true only
Q_accuracy_true <- df_political_true %>% filter(measurement == "Acc_Abs")
Q_accuracy_true <- Q_accuracy_true[["value"]]
Q_accuracy_true <- quantile(Q_accuracy_true, probs=c(.25, .75), na.rm = FALSE)

IQR_accuracy_true <- df_political_true %>% filter(measurement == "Acc_Abs")
IQR_accuracy_true <- IQR_accuracy_true[["value"]]
IQR_accuracy_true <- IQR(Q_accuracy_true)

up_accuracy_true <-  Q_accuracy_true[2]+1.5*IQR_accuracy_true # Upper Range  
low_accuracy_true <- Q_accuracy_true[1]-1.5*IQR_accuracy_true # Lower Range  

c_df_political_true_abs <- df_political_true %>% filter(measurement == "Acc_Abs")
c_df_political_true_abs$value[c_df_political_true_abs$value < low_accuracy_true[[1]]] <- NA
c_df_political_true_abs$value[c_df_political_true_abs$value > up_accuracy_true[[1]]] <- NA

index_remove_true <- is.na(c_df_political_true_abs$value)
index_remove_true <- c_df_political_true_abs$`Item #`[index_remove_true]

#political false only
Q_accuracy_false <- df_political_false %>% filter(measurement == "Acc_Abs")
Q_accuracy_false <- Q_accuracy_false[["value"]]
Q_accuracy_false <- quantile(Q_accuracy_false, probs=c(.25, .75), na.rm = FALSE)

IQR_accuracy_false <- df_political_false %>% filter(measurement == "Acc_Abs")
IQR_accuracy_false <- IQR_accuracy_false[["value"]]
IQR_accuracy_false <- IQR(Q_accuracy_false)

up_accuracy_false <-  Q_accuracy_false[2]+1.5*IQR_accuracy_false # Upper Range  
low_accuracy_false <- Q_accuracy_false[1]-1.5*IQR_accuracy_false # Lower Range

c_df_political_false_abs <- df_political_false %>% filter(measurement == "Acc_Abs")
c_df_political_false_abs$value[c_df_political_false_abs$value < low_accuracy_false[[1]]] <- NA
c_df_political_false_abs$value[c_df_political_false_abs$value > up_accuracy_false[[1]]] <- NA

index_remove_false <- is.na(c_df_political_false_abs$value)
index_remove_false <- c_df_political_false_abs$`Item #`[index_remove_false]

index_remove_all <- c(index_remove_true, index_remove_false)
index_remove_all <- unique(index_remove_all)
# index_remove_all

`%notin%` <- Negate(`%in%`)
# after identifying which items to remove now creating new corrected dfs
c_df_political <- df_political %>% filter(`Item #` %notin% index_remove_all)


#political true only
c_df_political_true <- c_df_political %>% filter(Category == "Political_True" | Category == "COVID_True")

#political false only
c_df_political_false <- c_df_political %>% filter(Category == "Political_Fake" | Category == "COVID_Fake")

```


# Clean Descriptives across the categories (Political_True and _False)
```{r descriptives across cateogires clean}
c_df_political %>% group_by(Category, measurement) %>%
  summarise(mean = mean(value), SD = sd(value), count = n(), se = (SD/(sqrt(count))), median = median(value), min = min(value), max = max(value))

# Basic histogram Absolute Accuracy
c_df_political %>% filter(measurement == "Acc_Abs") %>% ggplot(aes(x=value)) + geom_histogram() + theme_apa() + labs(title = "Accuracy Histogram - Percentage", x = "Percentage Values", y = "Count",  subtitle = "For all values collapsed across political leaning and items") + geom_vline(aes(xintercept = mean(value)), linetype="dashed") 

# Basic boxplot Absolute Accuracy
c_df_political %>% filter(measurement == "Acc_Abs") %>% ggplot(aes(x=value)) + geom_boxplot() + theme_apa() + labs(title = "Accuracy Boxplot - Percentage", x = "Percentage Values", y = "Count",  subtitle = "For all values collapsed across political leaning and items")

# Basic histogram Absolute Accuracy
c_df_political %>% filter(measurement == "Acc_Abs") %>% ggplot(aes(x=value)) + geom_histogram() + theme_apa() + labs(title = "Accuracy Histogram - Percentage", x = "Percentage Values", y = "Count", subtitle = "Grouped by all categories, collapsed acorss political leaning") + facet_wrap(~Category)

# Basic boxplot Absolute Accuracy
c_df_political %>% filter(measurement == "Acc_Abs") %>% ggplot(aes(x=value)) + geom_boxplot() + theme_apa() + labs(title = "Accuracy Boxplot - Percentage", x = "Percentage Values", y = "Count",  subtitle = "For all values collapsed across political leaning and items") + facet_wrap(~Category)


# Basic histogram Relative Accuracy
c_df_political %>% filter(measurement == "Acc") %>% ggplot(aes(x=value)) + geom_histogram() + theme_apa() + labs(title = "Accuracy Histogram - Likert means", x = "Likert Values", y = "Count",  subtitle = "For all values collapsed across political leaning and items \n 1: extremely unlikely; 6 extremely likely") + geom_vline(aes(xintercept = mean(value)), linetype="dashed") 

# Basic histogram Relative Accuracy
c_df_political %>% filter(measurement == "Acc") %>% ggplot(aes(x=value)) + geom_histogram() + theme_apa() + labs(title = "Accuracy Histogram - Likert means", x = "Likert Values", y = "Count", subtitle = "Collapsed acorss political leaning \n 1: extremely unlikely; 6 extremely likely") + facet_wrap(~Category)

# Basic histogram Familiarity 
c_df_political %>% filter(measurement == "Fam") %>% ggplot(aes(x=value)) + geom_histogram() + theme_apa() + labs(title = "Familiarity Histogram - Likert means", x = "Likert Values", y = "Count",  subtitle = "For all values collapsed across political leaning and items \n 1: not at all; 6 extremely") + geom_vline(aes(xintercept = mean(value)), linetype="dashed")

# Basic histogram Familiarity
c_df_political %>% filter(measurement == "Fam") %>% ggplot(aes(x=value)) + geom_histogram() + theme_apa() + labs(title = "Familiarity Histogram - Likert means", x = "Likert Values", y = "Count", subtitle = "Collapsed acorss political leaning \n 1: not at all; 6 extremely") + facet_wrap(~Category)

```


# Clean Descriptives across the _True only
```{r descriptives Political True only clean}
c_df_political_true %>% group_by(Category, political_leaning, measurement) %>%
  summarise(mean = mean(value), SD = sd(value), count = n(), se = (SD/(sqrt(count))), median = median(value), min = min(value), max = max(value))

# Basic histogram Absolute Accuracy
c_df_political_true %>% filter(measurement == "Acc_Abs") %>% ggplot(aes(x=value, fill = Category)) + geom_histogram() + theme_apa() + labs(title = "Accuracy Histogram - Percentage", x = "Percentage Values", y = "Count", subtitle = "For _True only, collapsed across political leaning") + geom_vline(aes(xintercept = mean(value)), linetype="dashed") 

# Basic histogram Absolute Accuracy
c_df_political_true %>% filter(measurement == "Acc_Abs") %>% ggplot(aes(x=value, fill = Category)) + geom_histogram() + theme_apa() + labs(title = "Accuracy Histogram - Percentage", x = "Percentage Values", y = "Count", subtitle = "For _True only") + facet_wrap(~political_leaning)

# Basic histogram Relative Accuracy
c_df_political_true %>% filter(measurement == "Acc") %>% ggplot(aes(x=value, fill = Category)) + geom_histogram() + theme_apa() + labs(title = "Accuracy Histogram - Likert means", x = "Likert Values", y = "Count", subtitle = "For _True only, collapsed across political leaning \n 1: extremely unlikely; 6 extremely likely") + geom_vline(aes(xintercept = mean(value)), linetype="dashed") 

# Basic histogram Relative Accuracy
c_df_political_true %>% filter(measurement == "Acc") %>% ggplot(aes(x=value, fill = Category)) + geom_histogram() + theme_apa() + labs(title = "Accuracy Histogram - Likert means", x = "Likert Values", y = "Count", subtitle = "For _True only \n 1: extremely unlikely; 6 extremely likely") + facet_wrap(~political_leaning)

# Basic histogram Familiarity 
c_df_political_true %>% filter(measurement == "Fam") %>% ggplot(aes(x=value, fill = Category)) + geom_histogram() + theme_apa() + labs(title = "Familiarity Histogram - Likert means", x = "Likert Values", y = "Count", subtitle = "For _True only, collapsed across political leaning \n 1: not at all; 6 extremely") + geom_vline(aes(xintercept = mean(value)), linetype="dashed") 

# Basic histogram Familiarity
c_df_political_true %>% filter(measurement == "Fam") %>% ggplot(aes(x=value, fill = Category)) + geom_histogram() + theme_apa() + labs(title = "Familiarity Histogram - Likert means", x = "Likert Values", y = "Count", subtitle = "For _True only \n 1: not at all; 6 extremely") + facet_wrap(~political_leaning)

```


# Clean Descriptives across the Political_False only
```{r descriptives Political False only clean}
c_df_political_false %>% group_by(Category, political_leaning, measurement) %>%
  summarise(mean = mean(value), SD = sd(value), count = n(), se = (SD/(sqrt(count))), median = median(value), min = min(value), max = max(value))

# Basic histogram Absolute Accuracy
c_df_political_false %>% filter(measurement == "Acc_Abs") %>% ggplot(aes(x=value, fill = Category)) + geom_histogram() + theme_apa() + labs(title = "Accuracy Histogram - Percentage", x = "Percentage Values", y = "Count", subtitle = "For _False only, collapsed across political leaning") + geom_vline(aes(xintercept = mean(value)), linetype="dashed")

# Basic histogram Absolute Accuracy
c_df_political_false %>% filter(measurement == "Acc_Abs") %>% ggplot(aes(x=value, fill = Category)) + geom_histogram() + theme_apa() + labs(title = "Accuracy Histogram - Percentage", x = "Percentage Values", y = "Count", subtitle = "For _False only") + facet_wrap(~political_leaning)

# Basic histogram Relative Accuracy
c_df_political_false %>% filter(measurement == "Acc") %>% ggplot(aes(x=value, fill = Category)) + geom_histogram() + theme_apa() + labs(title = "Accuracy Histogram - Likert means", x = "Likert Values", y = "Count", subtitle = "For _False only, collapsed across political leaning \n 1: extremely unlikely; 6 extremely likely") + geom_vline(aes(xintercept = mean(value)), linetype="dashed")

# Basic histogram Relative Accuracy
c_df_political_false %>% filter(measurement == "Acc") %>% ggplot(aes(x=value, fill = Category)) + geom_histogram() + theme_apa() + labs(title = "Accuracy Histogram - Likert means", x = "Likert Values", y = "Count", subtitle = "For _False only \n 1: extremely unlikely; 6 extremely likely") + facet_wrap(~political_leaning)

# Basic histogram Familiarity 
c_df_political_false %>% filter(measurement == "Fam") %>% ggplot(aes(x=value, fill = Category)) + geom_histogram() + theme_apa() + labs(title = "Familiarity Histogram - Likert means", x = "Likert Values", y = "Count", subtitle = "For _False only, collapsed across political leaning \n 1: not at all; 6 extremely") + geom_vline(aes(xintercept = mean(value)), linetype="dashed") 

# Basic histogram Familiarity
c_df_political_false %>% filter(measurement == "Fam") %>% ggplot(aes(x=value, fill = Category)) + geom_histogram() + theme_apa() + labs(title = "Familiarity Histogram - Likert means", x = "Likert Values", y = "Count", subtitle = "For _False only \n 1: not at all; 6 extremely") + facet_wrap(~political_leaning)

```

# Item selection (politically true only)
## all items, no familiarity thershold (political_true only)
```{r picking items on the basis of different levels of familarity - true only}
#all familiarity
c_df_political_true %>% filter(measurement == "Fam") %>%
  ggplot() + geom_bar(aes(x = `Image Name`, y = value, fill = Par_Combined), stat = 'identity', position = 'dodge') + theme_apa(legend.use.title = TRUE) + theme(axis.text.x = element_text(angle = 45, hjust = 1, size = 4)) + labs(title = "All items, all familiarity", x = "Image Name", y = "Familiarity", fill = "Item Pol. Leaning") + scale_fill_manual(values=c("#0021F5", "#EA3223"))

accuracy_all_fam <- c_df_political_true %>% filter(measurement == "Acc_Abs") %>% group_by(political_leaning, Par_Combined) %>% summarise(mean = mean(value), SD = sd(value), count = n(), se = (SD/(sqrt(count))), median = median(value), min = min(value), max = max(value))
accuracy_all_fam

accuracy_all_fam <- c_df_political_true %>% filter(measurement == "Acc_Abs") %>% group_by(Category, political_leaning, Par_Combined) %>% summarise(mean = mean(value), SD = sd(value), count = n(), se = (SD/(sqrt(count))), median = median(value), min = min(value), max = max(value))
accuracy_all_fam

#making table
# accuracy_all_fam_table <- accuracy_all_fam[1:4,-1]

accuracy_all_fam %>%
  ggplot(aes(x = Par_Combined, y = mean, fill = as.factor(political_leaning))) + 
  geom_bar(stat = 'identity', position = 'dodge') + theme_apa(legend.use.title = TRUE) + labs(title ="Accuracy across Dem and Rep favoured items", x = "Item Political Leaning", y = "Percent Accuracy", fill = "Pps Political Leaning") + scale_fill_manual(values=c("#0021F5", "#EA3223"))

accuracy_all_fam %>%
  ggplot(aes(x = Par_Combined, y = mean, fill = as.factor(political_leaning))) + 
  geom_bar(stat = 'identity', position = 'dodge') + geom_errorbar(aes(ymin = mean-se, ymax =mean + se), width = .2, position = position_dodge(.9)) + theme_apa(legend.use.title = TRUE) + labs(title ="Accuracy across Dem and Rep favoured items", x = "Item Political Leaning", y = "Percent Accuracy", fill = "Pps Political Leaning") + scale_fill_manual(values=c("#0021F5", "#EA3223")) + facet_wrap(~Category)


```

# Item selection (politically false only)
## all items, no familiarity thershold (political_false only)
```{r picking items on the basis of different levels of familarity - false only}
#all familiarity
c_df_political_false %>% filter(measurement == "Fam") %>%
  ggplot() + geom_bar(aes(x = `Image Name`, y = value, fill = Par_Combined), stat = 'identity', position = 'dodge') + theme_apa(legend.use.title = TRUE) + theme(axis.text.x = element_text(angle = 45, hjust = 1, size = 4)) + labs(title = "All items, all familiarity", x = "Image Name", y = "Familiarity", fill = "Item Pol. Leaning") + scale_fill_manual(values=c("#0021F5", "#EA3223"))


accuracy_all_fam <- c_df_political_false %>% filter(measurement == "Acc_Abs") %>% group_by(political_leaning, Par_Combined) %>% summarise(mean = mean(value), SD = sd(value), count = n(), se = (SD/(sqrt(count))), median = median(value), min = min(value), max = max(value))
accuracy_all_fam

accuracy_all_fam <- c_df_political_false %>% filter(measurement == "Acc_Abs") %>% group_by(Category, political_leaning, Par_Combined) %>% summarise(mean = mean(value), SD = sd(value), count = n(), se = (SD/(sqrt(count))), median = median(value), min = min(value), max = max(value))
accuracy_all_fam

accuracy_all_fam %>%
  ggplot(aes(x = Par_Combined, y = mean, fill = as.factor(political_leaning))) + 
  geom_bar(stat = 'identity', position = 'dodge') + theme_apa(legend.use.title = TRUE) + labs(title ="Accuracy across Dem and Rep favoured items", x = "Item Political Leaning", y = "Percent Accuracy", fill = "Pps Political Leaning") + scale_fill_manual(values=c("#0021F5", "#EA3223"))

accuracy_all_fam %>%
  ggplot(aes(x = Par_Combined, y = mean, fill = as.factor(political_leaning))) + 
  geom_bar(stat = 'identity', position = 'dodge') + geom_errorbar(aes(ymin = mean-se, ymax =mean + se), width = .2, position = position_dodge(.9)) + theme_apa(legend.use.title = TRUE) + labs(title ="Accuracy across Dem and Rep favoured items", x = "Item Political Leaning", y = "Percent Accuracy", fill = "Pps Political Leaning") + scale_fill_manual(values=c("#0021F5", "#EA3223")) + facet_wrap(~Category)


```


```{r}
#  final selection
# View(c_df_political_true %>% filter(measurement == "Fam", Par_Combined == "Dem Favoured", political_leaning == "Democrat"))

tmp <- c_df_political_true %>% filter(measurement == "Fam", Par_Combined == "Dem Favoured", political_leaning == "Democrat")

tmp <- rbind(tmp, c_df_political_true %>% filter(measurement == "Fam", Par_Combined == "Rep Favoured", political_leaning == "Democrat"))

tmp <- rbind(tmp, c_df_political_false %>% filter(measurement == "Fam", Par_Combined == "Dem Favoured", political_leaning == "Democrat"))

tmp <- rbind(tmp, c_df_political_false %>% filter(measurement == "Fam", Par_Combined == "Rep Favoured", political_leaning == "Democrat"))

write_xlsx(
  tmp,
  path = "item_selection - review(1).xlsx",
  col_names = TRUE)
```

# Partisian 
```{r preparing df to run histograms for political leaning}

# removing unnecessary columns
df_slim_leaning <- df[, c("Item #", "Category", "Image Name", "Headline Summary", "Par_Dem", "Par_Rep", "Par_Combined")]

#add whether the items are democratic favoured or republican favoured
df_slim_leaning$Par_Combined_Categ <- ifelse(df_slim_leaning$Par_Combined > 3.5, "Rep Favoured", "Dem Favoured")

# long format
df_slim_leaning_long <- gather(df_slim_leaning, key = "measurement", value = "value", -c("Item #", "Category", "Image Name", "Headline Summary", "Par_Combined_Categ"))

# adding political variable
df_slim_leaning_long$political_leaning <- "Democrat"

df_slim_leaning_long$political_leaning <- ifelse(str_detect(df_slim_leaning_long$measurement, "Rep") == TRUE, df_slim_leaning_long$political_leaning <- "Republican", df_slim_leaning_long$political_leaning <- "Democrat")

df_slim_leaning_long$political_leaning[str_detect(df_slim_leaning_long$measurement, "Combined")] <- "Combined"
df_slim_leaning_long$Par_Combined_Categ[str_detect(df_slim_leaning_long$measurement, "Combined")] <- "Combined"

df_slim_leaning_long$measurement <- str_replace(df_slim_leaning_long$measurement, c("_Rep"), "")
df_slim_leaning_long$measurement <- str_replace(df_slim_leaning_long$measurement, c("_Dem"), "")
df_slim_leaning_long$measurement <- str_replace(df_slim_leaning_long$measurement, c("_Combined"), "")

#adding classes
df_slim_leaning_long$Par_Combined_Categ <- factor(df_slim_leaning_long$Par_Combined_Categ, levels = c("Dem Favoured", "Rep Favoured", "Combined"))

# df_slim_leaning_long <- df_slim_leaning_long %>% filter(Category == "Political_True" | Category == "Political_Fake")

# removing those high or low in accuracy 
# after identifying which items to remove now creating new corrected dfs
df_slim_leaning_long <- df_slim_leaning_long %>% filter(`Item #` %notin% index_remove_all)

```

```{r histograms partisanship}

df_slim_leaning_long %>% group_by(Category, political_leaning) %>%
  summarise(mean = mean(value), SD = sd(value), count = n(), se = (SD/(sqrt(count))), median = median(value), min = min(value), max = max(value))

# Basic histogram partisanship combined
df_slim_leaning_long %>% filter(political_leaning == "Combined") %>% ggplot(aes(x=value)) + geom_histogram() + theme_apa() + labs(title = "Partisanship - Combined", x = "Likert Values", y = "Count",  subtitle = "If accurate, how favorable to Democrats vs. Republicans (>= 4: Rep)") + geom_vline(aes(xintercept = mean(value)), linetype="dashed") + ylim(0,18)

# Basic histogram partisanship combined facet
df_slim_leaning_long %>% filter(political_leaning == "Combined") %>% ggplot(aes(x=value)) + geom_histogram() + theme_apa() + labs(title = "Partisanship - Combined", x = "Likert Values", y = "Count",  subtitle = "If accurate, how favorable to Democrats vs. Republicans (>= 4: Rep)") + facet_wrap(~Category) + ylim(0,18)

# Basic histogram partisanship dems only
df_slim_leaning_long %>% filter(political_leaning == "Democrat") %>% ggplot(aes(x=value)) + geom_histogram() + theme_apa() + labs(title = "Partisanship - Democrats Only", x = "Likert Values", y = "Count",  subtitle = "If accurate, how favorable to Democrats vs. Republicans (>= 4: Rep)") + geom_vline(aes(xintercept = mean(value)), linetype="dashed") + ylim(0,18)

# Basic histogram partisanship dems only facet
df_slim_leaning_long %>% filter(political_leaning == "Democrat") %>% ggplot(aes(x=value)) + geom_histogram() + theme_apa() + labs(title = "Partisanship - Democrats Only", x = "Likert Values", y = "Count",  subtitle = "If accurate, how favorable to Democrats vs. Republicans (>= 4: Rep)") + facet_wrap(~Category) + ylim(0,18)

# Basic histogram partisanship reps
df_slim_leaning_long %>% filter(political_leaning == "Republican") %>% ggplot(aes(x=value)) + geom_histogram() + theme_apa() + labs(title = "Partisanship - Republicans Only", x = "Likert Values", y = "Count",  subtitle = "If accurate, how favorable to Democrats vs. Republicans (>= 4: Rep)") + geom_vline(aes(xintercept = mean(value)), linetype="dashed") + ylim(0,18)

# Basic histogram partisanship reps facet
df_slim_leaning_long %>% filter(political_leaning == "Republican") %>% ggplot(aes(x=value)) + geom_histogram() + theme_apa() + labs(title = "Partisanship - Republicans Only", x = "Likert Values", y = "Count",  subtitle = "If accurate, how favorable to Democrats vs. Republicans (>= 4: Rep)") + facet_wrap(~Category) + ylim(0,18)

# Basic histogram all partisanship factors
df_slim_leaning_long %>% ggplot(aes(x=value)) + geom_histogram() + theme_apa() + labs(title = "Partisanship - All factors", x = "Likert Values", y = "Count",  subtitle = "If accurate, how favorable to Democrats vs. Republicans (>= 4: Rep)") + facet_wrap(~political_leaning)

```
```{r removing items to create 96 item dataset}

final_set <- df_slim_leaning_long
final_set_tmp <- df_slim_leaning_long %>% filter(Par_Combined_Categ == "Combined")

final_set_tmp <- final_set_tmp %>% filter(value < 3.4 | value > 3.6)

final_set_index <- final_set_tmp$`Item #`

c_df_political_final_set <- c_df_political %>% filter(measurement == "Acc_Abs", political_leaning == "Democrat")
c_df_political_final_set <- c_df_political_final_set %>%  filter(`Item #` %in% final_set_index)

c_df_political_final_set$True_Fake <- "Fake"
tmp_index <- str_detect(c_df_political_final_set$Category, "_True")
c_df_political_final_set$True_Fake[tmp_index] <- "True"

c_df_political_final_set_summary <- c_df_political_final_set %>% filter(measurement == "Acc_Abs") %>% group_by(True_Fake, Par_Combined) %>% summarise(mean = mean(value), SD = sd(value), count = n(), se = (SD/(sqrt(count))), median = median(value), min = min(value), max = max(value))

c_df_political_final_set_summary

```

```{r create final set of 27}

#true dem
final_true_dem <- c_df_political_final_set %>% filter(True_Fake == "True", Par_Combined == "Dem Favoured")
rand_samp <- sample(nrow(final_true_dem),27)
rand_samp
final_true_dem <- final_true_dem[rand_samp,]


#true rep
final_true_rep <- c_df_political_final_set %>% filter(True_Fake == "True", Par_Combined == "Rep Favoured")
rand_samp <- sample(nrow(final_true_rep),27)
rand_samp
final_true_rep <- final_true_rep[rand_samp,]

#false dem
final_false_dem <- c_df_political_final_set %>% filter(True_Fake == "Fake", Par_Combined == "Dem Favoured")
rand_samp <- sample(nrow(final_false_dem),27)
rand_samp
final_false_dem <- final_false_dem[rand_samp,]

#false rep
final_false_rep <- c_df_political_final_set %>% filter(True_Fake == "Fake", Par_Combined == "Rep Favoured")
rand_samp <- sample(nrow(final_false_rep),27)
rand_samp
final_false_rep <- final_false_rep[rand_samp,]

final_all <- rbind(final_true_dem,final_true_rep, final_false_dem, final_false_rep)

write_xlsx(
  final_all,
  path = "final_all.xlsx",
  col_names = TRUE)

```

