---
title: "Item Selection"
author: "Mubashir Sultan"
date: "2/17/2021"
output:
  html_document: default
  pdf_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r libraries and initial setup,  include=FALSE}
#loading libraries
library(readr)
library(readxl)
library(writexl)
library(tidyverse)
library(jtools)
```

```{r loading dataset,  include=FALSE}
rm(list=ls());

# reading excel sheet
df <- read_excel("/Users/mubashirsultan/Dropbox/partisanship selection example_RP2.xlsx", sheet = 1, col_names = TRUE, col_types = NULL)

# removing unnecessary columns
df_slim <- df[, c("Item #", "Category", "Image Name", "Headline Summary", "Acc_Abs_Dem", "Acc_Abs_Rep","Acc_Dem", "Acc_Rep", "Fam_Dem", "Fam_Rep", "Par_Combined")]

#add whether the items are democratic favoured or republican favoured
df_slim$Par_Combined <- ifelse(df_slim$Par_Combined > 3.5, "Rep Favoured", "Dem Favoured")

# long format
df_slim_long <- gather(df_slim, key = "measurement", value = "value", -c("Item #", "Category", "Image Name", "Headline Summary", "Par_Combined"))

# adding political variable
df_slim_long$political_leaning <- "Democrat"

df_slim_long$political_leaning <- ifelse(str_detect(df_slim_long$measurement, "Rep") == TRUE, df_slim_long$political_leaning <- "Republican", df_slim_long$political_leaning <- "Democrat")

df_slim_long$measurement <- str_replace(df_slim_long$measurement, c("_Rep"), "")
df_slim_long$measurement <- str_replace(df_slim_long$measurement, c("_Dem"), "")

#adding classes
df_slim_long$measurement <- factor(df_slim_long$measurement, levels = c("Acc_Abs", "Acc", "Fam", ""))
df_slim_long$Par_Combined <- factor(df_slim_long$Par_Combined, levels = c("Dem Favoured", "Rep Favoured"))

```


```{r creating political df,  include=FALSE}
df_political <- df_slim_long %>% filter(Category == "Political_True" | Category == "Political_Fake")

#political true only
df_political_true <- df_slim_long %>% filter(Category == "Political_True")

#political false only
df_political_false <- df_slim_long %>% filter(Category == "Political_Fake")
```

# Descriptives across the categories (Political_True and _False)
```{r descriptives across cateogires}
df_political %>% group_by(Category, measurement) %>%
  summarise(mean = mean(value), SD = sd(value), count = n(), se = (SD/(sqrt(count))), median = median(value), min = min(value), max = max(value))

# Basic histogram Absolute Accuracy
df_political %>% filter(measurement == "Acc_Abs") %>% ggplot(aes(x=value)) + geom_histogram() + theme_apa() + labs(title = "Accuracy Histogram - Percentage", x = "Percentage Values", y = "Count",  subtitle = "For all values collapsed across political leaning and true vs false news") + geom_vline(aes(xintercept = mean(value)), linetype="dashed") 

# Basic boxplot Absolute Accuracy
df_political %>% filter(measurement == "Acc_Abs") %>% ggplot(aes(x=value)) + geom_boxplot() + theme_apa() + labs(title = "Accuracy Boxplot - Percentage", x = "Percentage Values", y = "Count",  subtitle = "For all values collapsed across political leaning and true vs false news")

# Basic histogram Absolute Accuracy
df_political %>% filter(measurement == "Acc_Abs") %>% ggplot(aes(x=value)) + geom_histogram() + theme_apa() + labs(title = "Accuracy Histogram - Percentage", x = "Percentage Values", y = "Count", subtitle = "Grouped by true vs false news, collapsed acorss political leaning") + facet_wrap(~Category)

# Basic boxplot Absolute Accuracy
df_political %>% filter(measurement == "Acc_Abs") %>% ggplot(aes(x=value)) + geom_boxplot() + theme_apa() + labs(title = "Accuracy Boxplot - Percentage", x = "Percentage Values", y = "Count",  subtitle = "For all values collapsed across political leaning and true vs false news") + facet_wrap(~Category)


# Basic histogram Relative Accuracy
df_political %>% filter(measurement == "Acc") %>% ggplot(aes(x=value)) + geom_histogram() + theme_apa() + labs(title = "Accuracy Histogram - Likert means", x = "Likert Values", y = "Count",  subtitle = "For all values collapsed across political leaning and true vs false news \n 1: extremely unlikely; 6 extremely likely") + geom_vline(aes(xintercept = mean(value)), linetype="dashed") 

# Basic histogram Relative Accuracy
df_political %>% filter(measurement == "Acc") %>% ggplot(aes(x=value)) + geom_histogram() + theme_apa() + labs(title = "Accuracy Histogram - Likert means", x = "Likert Values", y = "Count", subtitle = "Collapsed acorss political leaning \n 1: extremely unlikely; 6 extremely likely") + facet_wrap(~Category)

# Basic histogram Familiarity 
df_political %>% filter(measurement == "Fam") %>% ggplot(aes(x=value)) + geom_histogram() + theme_apa() + labs(title = "Familiarity Histogram - Likert means", x = "Likert Values", y = "Count",  subtitle = "For all values collapsed across political leaning and true vs false news \n 1: not at all; 6 extremely") + geom_vline(aes(xintercept = mean(value)), linetype="dashed")

# Basic histogram Familiarity
df_political %>% filter(measurement == "Fam") %>% ggplot(aes(x=value)) + geom_histogram() + theme_apa() + labs(title = "Familiarity Histogram - Likert means", x = "Likert Values", y = "Count", subtitle = "Collapsed acorss political leaning \n 1: not at all; 6 extremely") + facet_wrap(~Category)

```


# Descriptives across the Political_True only
```{r descriptives Political True only}
df_political_true %>% group_by(political_leaning, measurement) %>%
  summarise(mean = mean(value), SD = sd(value), count = n(), se = (SD/(sqrt(count))), median = median(value), min = min(value), max = max(value))

# Basic histogram Absolute Accuracy
df_political_true %>% filter(measurement == "Acc_Abs") %>% ggplot(aes(x=value)) + geom_histogram() + theme_apa() + labs(title = "Accuracy Histogram - Percentage", x = "Percentage Values", y = "Count", subtitle = "For Political_True only, collapsed across political leaning") + geom_vline(aes(xintercept = mean(value)), linetype="dashed") 

# Basic histogram Absolute Accuracy
df_political_true %>% filter(measurement == "Acc_Abs") %>% ggplot(aes(x=value)) + geom_histogram() + theme_apa() + labs(title = "Accuracy Histogram - Percentage", x = "Percentage Values", y = "Count", subtitle = "For Political_True only") + facet_wrap(~political_leaning)

# Basic histogram Relative Accuracy
df_political_true %>% filter(measurement == "Acc") %>% ggplot(aes(x=value)) + geom_histogram() + theme_apa() + labs(title = "Accuracy Histogram - Likert means", x = "Likert Values", y = "Count", subtitle = "For Political_True only, collapsed across political leaning \n 1: extremely unlikely; 6 extremely likely") + geom_vline(aes(xintercept = mean(value)), linetype="dashed") 

# Basic histogram Relative Accuracy
df_political_true %>% filter(measurement == "Acc") %>% ggplot(aes(x=value)) + geom_histogram() + theme_apa() + labs(title = "Accuracy Histogram - Likert means", x = "Likert Values", y = "Count", subtitle = "For Political_True only \n 1: extremely unlikely; 6 extremely likely") + facet_wrap(~political_leaning)

# Basic histogram Familiarity 
df_political_true %>% filter(measurement == "Fam") %>% ggplot(aes(x=value)) + geom_histogram() + theme_apa() + labs(title = "Familiarity Histogram - Likert means", x = "Likert Values", y = "Count", subtitle = "For Political_True only, collapsed across political leaning \n 1: not at all; 6 extremely") + geom_vline(aes(xintercept = mean(value)), linetype="dashed") 

# Basic histogram Familiarity
df_political_true %>% filter(measurement == "Fam") %>% ggplot(aes(x=value)) + geom_histogram() + theme_apa() + labs(title = "Familiarity Histogram - Likert means", x = "Likert Values", y = "Count", subtitle = "For Political_True only \n 1: not at all; 6 extremely") + facet_wrap(~political_leaning)

```


# Descriptives across the Political_False only
```{r descriptives Political False only}
df_political_false %>% group_by(political_leaning, measurement) %>%
  summarise(mean = mean(value), SD = sd(value), count = n(), se = (SD/(sqrt(count))), median = median(value), min = min(value), max = max(value))

# Basic histogram Absolute Accuracy
df_political_false %>% filter(measurement == "Acc_Abs") %>% ggplot(aes(x=value)) + geom_histogram() + theme_apa() + labs(title = "Accuracy Histogram - Percentage", x = "Percentage Values", y = "Count", subtitle = "For Political_False only, collapsed across political leaning") + geom_vline(aes(xintercept = mean(value)), linetype="dashed")

# Basic histogram Absolute Accuracy
df_political_false %>% filter(measurement == "Acc_Abs") %>% ggplot(aes(x=value)) + geom_histogram() + theme_apa() + labs(title = "Accuracy Histogram - Percentage", x = "Percentage Values", y = "Count", subtitle = "For Political_False only") + facet_wrap(~political_leaning)

# Basic histogram Relative Accuracy
df_political_false %>% filter(measurement == "Acc") %>% ggplot(aes(x=value)) + geom_histogram() + theme_apa() + labs(title = "Accuracy Histogram - Likert means", x = "Likert Values", y = "Count", subtitle = "For Political_False only, collapsed across political leaning \n 1: extremely unlikely; 6 extremely likely") + geom_vline(aes(xintercept = mean(value)), linetype="dashed")

# Basic histogram Relative Accuracy
df_political_false %>% filter(measurement == "Acc") %>% ggplot(aes(x=value)) + geom_histogram() + theme_apa() + labs(title = "Accuracy Histogram - Likert means", x = "Likert Values", y = "Count", subtitle = "For Political_False only \n 1: extremely unlikely; 6 extremely likely") + facet_wrap(~political_leaning)

# Basic histogram Familiarity 
df_political_false %>% filter(measurement == "Fam") %>% ggplot(aes(x=value)) + geom_histogram() + theme_apa() + labs(title = "Familiarity Histogram - Likert means", x = "Likert Values", y = "Count", subtitle = "For Political_False only, collapsed across political leaning \n 1: not at all; 6 extremely") + geom_vline(aes(xintercept = mean(value)), linetype="dashed") 

# Basic histogram Familiarity
df_political_false %>% filter(measurement == "Fam") %>% ggplot(aes(x=value)) + geom_histogram() + theme_apa() + labs(title = "Familiarity Histogram - Likert means", x = "Likert Values", y = "Count", subtitle = "For Political_False only \n 1: not at all; 6 extremely") + facet_wrap(~political_leaning)

```


```{r creating political df with values 3SD on accuracy removed,  include=FALSE}
# identifying outliers for accuracy - in both the political true and political false data

#political true only
Q_accuracy_true <- df_political_true %>% filter(measurement == "Acc_Abs")
Q_accuracy_true <- Q_accuracy_true[["value"]]
Q_accuracy_true <- quantile(Q_accuracy_true, probs=c(.25, .75), na.rm = FALSE)

IQR_accuracy_true <- df_political_true %>% filter(measurement == "Acc_Abs")
IQR_accuracy_true <- IQR_accuracy_true[["value"]]
IQR_accuracy_true <- IQR(Q_accuracy_true)

up_accuracy_true <-  Q_accuracy_true[2]+1.5*IQR_accuracy_true # Upper Range  
low_accuracy_true <- Q_accuracy_true[1]-1.5*IQR_accuracy_true # Lower Range  

c_df_political_true_abs <- df_political_true %>% filter(measurement == "Acc_Abs")
c_df_political_true_abs$value[c_df_political_true_abs$value < low_accuracy_true[[1]]] <- NA
c_df_political_true_abs$value[c_df_political_true_abs$value > up_accuracy_true[[1]]] <- NA

index_remove_true <- is.na(c_df_political_true_abs$value)
index_remove_true <- c_df_political_true_abs$`Item #`[index_remove_true]

#political false only
Q_accuracy_false <- df_political_false %>% filter(measurement == "Acc_Abs")
Q_accuracy_false <- Q_accuracy_false[["value"]]
Q_accuracy_false <- quantile(Q_accuracy_false, probs=c(.25, .75), na.rm = FALSE)

IQR_accuracy_false <- df_political_false %>% filter(measurement == "Acc_Abs")
IQR_accuracy_false <- IQR_accuracy_false[["value"]]
IQR_accuracy_false <- IQR(Q_accuracy_false)

up_accuracy_false <-  Q_accuracy_false[2]+1.5*IQR_accuracy_false # Upper Range  
low_accuracy_false <- Q_accuracy_false[1]-1.5*IQR_accuracy_false # Lower Range

c_df_political_false_abs <- df_political_false %>% filter(measurement == "Acc_Abs")
c_df_political_false_abs$value[c_df_political_false_abs$value < low_accuracy_false[[1]]] <- NA
c_df_political_false_abs$value[c_df_political_false_abs$value > up_accuracy_false[[1]]] <- NA

index_remove_false <- is.na(c_df_political_false_abs$value)
index_remove_false <- c_df_political_false_abs$`Item #`[index_remove_false]

index_remove_all <- c(index_remove_true, index_remove_false)
index_remove_all <- unique(index_remove_all)
# index_remove_all

`%notin%` <- Negate(`%in%`)
# after identifying which items to remove now creating new corrected dfs
c_df_political <- df_political %>% filter(`Item #` %notin% index_remove_all)


#political true only
c_df_political_true <- c_df_political %>% filter(Category == "Political_True")

#political false only
c_df_political_false <- c_df_political %>% filter(Category == "Political_Fake")

```


# Clean Descriptives across the categories (Political_True and _False)
```{r descriptives across cateogires clean}
c_df_political %>% group_by(Category, measurement) %>%
  summarise(mean = mean(value), SD = sd(value), count = n(), se = (SD/(sqrt(count))), median = median(value), min = min(value), max = max(value))

# Basic histogram Absolute Accuracy
c_df_political %>% filter(measurement == "Acc_Abs") %>% ggplot(aes(x=value)) + geom_histogram() + theme_apa() + labs(title = "Accuracy Histogram - Percentage", x = "Percentage Values", y = "Count",  subtitle = "For all values collapsed across political leaning and true vs false news") + geom_vline(aes(xintercept = mean(value)), linetype="dashed") 

# Basic boxplot Absolute Accuracy
c_df_political %>% filter(measurement == "Acc_Abs") %>% ggplot(aes(x=value)) + geom_boxplot() + theme_apa() + labs(title = "Accuracy Boxplot - Percentage", x = "Percentage Values", y = "Count",  subtitle = "For all values collapsed across political leaning and true vs false news")

# Basic histogram Absolute Accuracy
c_df_political %>% filter(measurement == "Acc_Abs") %>% ggplot(aes(x=value)) + geom_histogram() + theme_apa() + labs(title = "Accuracy Histogram - Percentage", x = "Percentage Values", y = "Count", subtitle = "Grouped by true vs false news, collapsed acorss political leaning") + facet_wrap(~Category)

# Basic boxplot Absolute Accuracy
c_df_political %>% filter(measurement == "Acc_Abs") %>% ggplot(aes(x=value)) + geom_boxplot() + theme_apa() + labs(title = "Accuracy Boxplot - Percentage", x = "Percentage Values", y = "Count",  subtitle = "For all values collapsed across political leaning and true vs false news") + facet_wrap(~Category)


# Basic histogram Relative Accuracy
c_df_political %>% filter(measurement == "Acc") %>% ggplot(aes(x=value)) + geom_histogram() + theme_apa() + labs(title = "Accuracy Histogram - Likert means", x = "Likert Values", y = "Count",  subtitle = "For all values collapsed across political leaning and true vs false news \n 1: extremely unlikely; 6 extremely likely") + geom_vline(aes(xintercept = mean(value)), linetype="dashed") 

# Basic histogram Relative Accuracy
c_df_political %>% filter(measurement == "Acc") %>% ggplot(aes(x=value)) + geom_histogram() + theme_apa() + labs(title = "Accuracy Histogram - Likert means", x = "Likert Values", y = "Count", subtitle = "Collapsed acorss political leaning \n 1: extremely unlikely; 6 extremely likely") + facet_wrap(~Category)

# Basic histogram Familiarity 
c_df_political %>% filter(measurement == "Fam") %>% ggplot(aes(x=value)) + geom_histogram() + theme_apa() + labs(title = "Familiarity Histogram - Likert means", x = "Likert Values", y = "Count",  subtitle = "For all values collapsed across political leaning and true vs false news \n 1: not at all; 6 extremely") + geom_vline(aes(xintercept = mean(value)), linetype="dashed")

# Basic histogram Familiarity
c_df_political %>% filter(measurement == "Fam") %>% ggplot(aes(x=value)) + geom_histogram() + theme_apa() + labs(title = "Familiarity Histogram - Likert means", x = "Likert Values", y = "Count", subtitle = "Collapsed acorss political leaning \n 1: not at all; 6 extremely") + facet_wrap(~Category)

```


# Clean Descriptives across the Political_True only
```{r descriptives Political True only clean}
c_df_political_true %>% group_by(political_leaning, measurement) %>%
  summarise(mean = mean(value), SD = sd(value), count = n(), se = (SD/(sqrt(count))), median = median(value), min = min(value), max = max(value))

# Basic histogram Absolute Accuracy
c_df_political_true %>% filter(measurement == "Acc_Abs") %>% ggplot(aes(x=value)) + geom_histogram() + theme_apa() + labs(title = "Accuracy Histogram - Percentage", x = "Percentage Values", y = "Count", subtitle = "For Political_True only, collapsed across political leaning") + geom_vline(aes(xintercept = mean(value)), linetype="dashed") 

# Basic histogram Absolute Accuracy
c_df_political_true %>% filter(measurement == "Acc_Abs") %>% ggplot(aes(x=value)) + geom_histogram() + theme_apa() + labs(title = "Accuracy Histogram - Percentage", x = "Percentage Values", y = "Count", subtitle = "For Political_True only") + facet_wrap(~political_leaning)

# Basic histogram Relative Accuracy
c_df_political_true %>% filter(measurement == "Acc") %>% ggplot(aes(x=value)) + geom_histogram() + theme_apa() + labs(title = "Accuracy Histogram - Likert means", x = "Likert Values", y = "Count", subtitle = "For Political_True only, collapsed across political leaning \n 1: extremely unlikely; 6 extremely likely") + geom_vline(aes(xintercept = mean(value)), linetype="dashed") 

# Basic histogram Relative Accuracy
c_df_political_true %>% filter(measurement == "Acc") %>% ggplot(aes(x=value)) + geom_histogram() + theme_apa() + labs(title = "Accuracy Histogram - Likert means", x = "Likert Values", y = "Count", subtitle = "For Political_True only \n 1: extremely unlikely; 6 extremely likely") + facet_wrap(~political_leaning)

# Basic histogram Familiarity 
c_df_political_true %>% filter(measurement == "Fam") %>% ggplot(aes(x=value)) + geom_histogram() + theme_apa() + labs(title = "Familiarity Histogram - Likert means", x = "Likert Values", y = "Count", subtitle = "For Political_True only, collapsed across political leaning \n 1: not at all; 6 extremely") + geom_vline(aes(xintercept = mean(value)), linetype="dashed") 

# Basic histogram Familiarity
c_df_political_true %>% filter(measurement == "Fam") %>% ggplot(aes(x=value)) + geom_histogram() + theme_apa() + labs(title = "Familiarity Histogram - Likert means", x = "Likert Values", y = "Count", subtitle = "For Political_True only \n 1: not at all; 6 extremely") + facet_wrap(~political_leaning)

```


# Clean Descriptives across the Political_False only
```{r descriptives Political False only clean}
c_df_political_false %>% group_by(political_leaning, measurement) %>%
  summarise(mean = mean(value), SD = sd(value), count = n(), se = (SD/(sqrt(count))), median = median(value), min = min(value), max = max(value))

# Basic histogram Absolute Accuracy
c_df_political_false %>% filter(measurement == "Acc_Abs") %>% ggplot(aes(x=value)) + geom_histogram() + theme_apa() + labs(title = "Accuracy Histogram - Percentage", x = "Percentage Values", y = "Count", subtitle = "For Political_False only, collapsed across political leaning") + geom_vline(aes(xintercept = mean(value)), linetype="dashed")

# Basic histogram Absolute Accuracy
c_df_political_false %>% filter(measurement == "Acc_Abs") %>% ggplot(aes(x=value)) + geom_histogram() + theme_apa() + labs(title = "Accuracy Histogram - Percentage", x = "Percentage Values", y = "Count", subtitle = "For Political_False only") + facet_wrap(~political_leaning)

# Basic histogram Relative Accuracy
c_df_political_false %>% filter(measurement == "Acc") %>% ggplot(aes(x=value)) + geom_histogram() + theme_apa() + labs(title = "Accuracy Histogram - Likert means", x = "Likert Values", y = "Count", subtitle = "For Political_False only, collapsed across political leaning \n 1: extremely unlikely; 6 extremely likely") + geom_vline(aes(xintercept = mean(value)), linetype="dashed")

# Basic histogram Relative Accuracy
c_df_political_false %>% filter(measurement == "Acc") %>% ggplot(aes(x=value)) + geom_histogram() + theme_apa() + labs(title = "Accuracy Histogram - Likert means", x = "Likert Values", y = "Count", subtitle = "For Political_False only \n 1: extremely unlikely; 6 extremely likely") + facet_wrap(~political_leaning)

# Basic histogram Familiarity 
c_df_political_false %>% filter(measurement == "Fam") %>% ggplot(aes(x=value)) + geom_histogram() + theme_apa() + labs(title = "Familiarity Histogram - Likert means", x = "Likert Values", y = "Count", subtitle = "For Political_False only, collapsed across political leaning \n 1: not at all; 6 extremely") + geom_vline(aes(xintercept = mean(value)), linetype="dashed") 

# Basic histogram Familiarity
c_df_political_false %>% filter(measurement == "Fam") %>% ggplot(aes(x=value)) + geom_histogram() + theme_apa() + labs(title = "Familiarity Histogram - Likert means", x = "Likert Values", y = "Count", subtitle = "For Political_False only \n 1: not at all; 6 extremely") + facet_wrap(~political_leaning)

```

# Item selection (politically true only)
## all items, no familiarity thershold (political_true only)
```{r picking items on the basis of different levels of familarity - true only}
#all familiarity
c_df_political_true %>% filter(measurement == "Fam") %>%
  ggplot() + geom_bar(aes(x = `Image Name`, y = value, fill = Par_Combined), stat = 'identity', position = 'dodge') + theme_apa(legend.use.title = TRUE) + theme(axis.text.x = element_text(angle = 45, hjust = 1, size = 4)) + labs(title = "All items, all familiarity", x = "Image Name", y = "Familiarity", fill = "Item Pol. Leaning") + scale_fill_manual(values=c("#0021F5", "#EA3223"))


accuracy_all_fam <- c_df_political_true %>% filter(measurement == "Acc_Abs") %>% group_by(political_leaning, Par_Combined) %>% summarise(mean = mean(value), SD = sd(value), count = n(), se = (SD/(sqrt(count))), median = median(value), min = min(value), max = max(value))
accuracy_all_fam

#making table
accuracy_all_fam_table <- accuracy_all_fam[1:2,-1]

accuracy_all_fam %>%
  ggplot(aes(x = Par_Combined, y = mean, fill = as.factor(political_leaning))) + 
  geom_bar(stat = 'identity', position = 'dodge') + geom_errorbar(aes(ymin = mean-se, ymax =mean + se), width = .2, position = position_dodge(.9)) + theme_apa(legend.use.title = TRUE) + labs(title ="Accuracy across Dem and Rep favoured items", x = "Item Political Leaning", y = "Percent Accuracy", fill = "Pps Political Leaning") + scale_fill_manual(values=c("#0021F5", "#EA3223"))


```

## all items, familiarity thershold < 3  (political_true only)
```{r picking items on the basis of different levels of familarity 3 - true only}
# limited to three
c_df_political_true %>% filter(measurement == "Fam", value < 3) %>%
  ggplot() + geom_bar(aes(x = `Image Name`, y = value, fill = Par_Combined), stat = 'identity', position = 'dodge') + theme_apa(legend.use.title = TRUE) + theme(axis.text.x = element_text(angle = 45, hjust = 1, size = 4)) + labs(title = "All items, familiarity < 3", x = "Image Name", y = "Familiarity", fill = "Item Pol. Leaning") + scale_fill_manual(values=c("#0021F5", "#EA3223"))

# need to find item numbers of those with Fam < 3 (across both dem and rep averaged)
# collapse across dem and rep - find average fam score, then exclude those that you don't need - make index from that.
accuracy_all_three_index <- c_df_political_true %>% group_by(`Item #`, `Image Name`, Par_Combined) %>% filter(measurement == "Fam") %>% summarise(mean = mean(value), SD = sd(value), count = n(), se = (SD/(sqrt(count))), median = median(value), min = min(value), max = max(value))

accuracy_all_three_index <- accuracy_all_three_index %>% filter(mean < 3)
accuracy_all_three_index <- accuracy_all_three_index[[1]]
# accuracy_all_three_index
# length(accuracy_all_three_index)

#given the index, now subset based on the index numbers.
accuracy_all_three <- c_df_political_true %>% filter(measurement == "Acc_Abs", `Item #` %in% accuracy_all_three_index) %>% group_by(political_leaning, Par_Combined) %>%
  summarise(mean = mean(value), SD = sd(value), count = n(), se = (SD/(sqrt(count))), median = median(value), min = min(value), max = max(value))
accuracy_all_three

#making table
accuracy_all_three_table <- accuracy_all_three[1:2,-1]

accuracy_all_three %>%
  ggplot(aes(x = Par_Combined, y = mean, fill = as.factor(political_leaning))) + 
  geom_bar(stat = 'identity', position = 'dodge') + geom_errorbar(aes(ymin = mean-se, ymax =mean + se), width = .2, position = position_dodge(.9)) + theme_apa(legend.use.title = TRUE) + labs(title ="Accuracy across Dem and Rep favoured items", x = "Item Political Leaning", y = "Percent Accuracy", fill = "Pps Political Leaning") + scale_fill_manual(values=c("#0021F5", "#EA3223"))

```

## all items,  familiarity thershold < 2.5  (political_true only)
```{r picking items on the basis of different levels of familarity 2.5 - true only}
# limited to 2.5
c_df_political_true %>% filter(measurement == "Fam", value < 2.5) %>%
  ggplot() + geom_bar(aes(x = `Image Name`, y = value, fill = Par_Combined), stat = 'identity', position = 'dodge') + theme_apa(legend.use.title = TRUE) + theme(axis.text.x = element_text(angle = 45, hjust = 1, size = 5)) + labs(title = "All items, familiarity < 2.5", x = "Image Name", y = "Familiarity", fill = "Item Pol. Leaning") + scale_fill_manual(values=c("#0021F5", "#EA3223"))

# need to find item numbers of those with Fam < 2.5 (across both dem and rep averaged)
# collapse across dem and rep - find average fam score, then exclude those that you don't need - make index from that.
accuracy_all_two.five <- c_df_political_true %>% group_by(`Item #`, `Image Name`, Par_Combined) %>% filter(measurement == "Fam") %>% summarise(mean = mean(value), SD = sd(value), count = n(), se = (SD/(sqrt(count))), median = median(value), min = min(value), max = max(value))

accuracy_all_two.five <- accuracy_all_two.five %>% filter(mean < 2.5)
accuracy_all_two.five <- accuracy_all_two.five[[1]]
# accuracy_all_two.five
# length(accuracy_all_two.five)

#given the index, now subset based on the index numbers.
accuracy_all_two.five <- c_df_political_true %>% filter(measurement == "Acc_Abs", `Item #` %in% accuracy_all_two.five) %>% group_by(political_leaning, Par_Combined) %>%
  summarise(mean = mean(value), SD = sd(value), count = n(), se = (SD/(sqrt(count))), median = median(value), min = min(value), max = max(value))
accuracy_all_two.five

#making table
accuracy_all_two.five_table <- accuracy_all_two.five[1:2,-1]

accuracy_all_two.five %>%
  ggplot(aes(x = Par_Combined, y = mean, fill = as.factor(political_leaning))) + 
  geom_bar(stat = 'identity', position = 'dodge') + geom_errorbar(aes(ymin = mean-se, ymax =mean + se), width = .2, position = position_dodge(.9)) + theme_apa(legend.use.title = TRUE) + labs(title ="Accuracy across Dem and Rep favoured items", x = "Item Political Leaning", y = "Percent Accuracy", fill = "Pps Political Leaning") + scale_fill_manual(values=c("#0021F5", "#EA3223"))

```

## all items, familiarity thershold < 2.4 (political_true only)
```{r picking items on the basis of different levels of familarity 2.4 - true only}
# limited to 2.4
c_df_political_true %>% filter(measurement == "Fam" , value < 2.4) %>%
  ggplot() + geom_bar(aes(x = `Image Name`, y = value, fill = Par_Combined), stat = 'identity', position = 'dodge') + theme_apa(legend.use.title = TRUE) + theme(axis.text.x = element_text(angle = 45, hjust = 1, size = 5)) + labs(title = "All items, familiarity < 2.4", x = "Image Name", y = "Familiarity", fill = "Item Pol. Leaning") + scale_fill_manual(values=c("#0021F5", "#EA3223"))

# need to find item numbers of those with Fam < 2.4 (across both dem and rep averaged)
# collapse across dem and rep - find average fam score, then exclude those that you don't need - make index from that.
accuracy_all_two.four <- c_df_political_true %>% group_by(`Item #`, `Image Name`, Par_Combined) %>% filter(measurement == "Fam") %>% summarise(mean = mean(value), SD = sd(value), count = n(), se = (SD/(sqrt(count))), median = median(value), min = min(value), max = max(value))

accuracy_all_two.four <- accuracy_all_two.four %>% filter(mean < 2.4)
accuracy_all_two.four <- accuracy_all_two.four[[1]]
# accuracy_all_two.four
# length(accuracy_all_two.four)

#given the index, now subset based on the index numbers.
accuracy_all_two.four <- c_df_political_true %>% filter(measurement == "Acc_Abs", `Item #` %in% accuracy_all_two.four) %>% group_by(political_leaning, Par_Combined) %>%
  summarise(mean = mean(value), SD = sd(value), count = n(), se = (SD/(sqrt(count))), median = median(value), min = min(value), max = max(value))
accuracy_all_two.four

#making table
accuracy_all_two.four_table <- accuracy_all_two.four[1:2,-1]

accuracy_all_two.four %>%
  ggplot(aes(x = Par_Combined, y = mean, fill = as.factor(political_leaning))) + 
  geom_bar(stat = 'identity', position = 'dodge') + geom_errorbar(aes(ymin = mean-se, ymax =mean + se), width = .2, position = position_dodge(.9)) + theme_apa(legend.use.title = TRUE) + labs(title ="Accuracy across Dem and Rep favoured items", x = "Item Political Leaning", y = "Percent Accuracy", fill = "Pps Political Leaning") + scale_fill_manual(values=c("#0021F5", "#EA3223"))
```

## all items, familiarity thershold < 2.3 (political_true only)
```{r picking items on the basis of different levels of familarity 2.3 - true only}
# limited to 2.3
c_df_political_true %>% filter(measurement == "Fam", value < 2.3) %>%
  ggplot() + geom_bar(aes(x = `Image Name`, y = value, fill = Par_Combined), stat = 'identity', position = 'dodge') + theme_apa(legend.use.title = TRUE) + theme(axis.text.x = element_text(angle = 45, hjust = 1, size = 6)) + labs(title = "All items, familiarity < 2.3", x = "Image Name", y = "Familiarity", fill = "Item Pol. Leaning") + scale_fill_manual(values=c("#0021F5", "#EA3223"))

# need to find item numbers of those with Fam < 2.3 (across both dem and rep averaged)
# collapse across dem and rep - find average fam score, then exclude those that you don't need - make index from that.
accuracy_all_two.three <- c_df_political_true %>% group_by(`Item #`, `Image Name`, Par_Combined) %>% filter(measurement == "Fam") %>% summarise(mean = mean(value), SD = sd(value), count = n(), se = (SD/(sqrt(count))), median = median(value), min = min(value), max = max(value))

accuracy_all_two.three <- accuracy_all_two.three %>% filter(mean < 2.3)
accuracy_all_two.three <- accuracy_all_two.three[[1]]
# accuracy_all_two.three
# length(accuracy_all_two.three)

#given the index, now subset based on the index numbers.
accuracy_all_two.three <- c_df_political_true %>% filter(measurement == "Acc_Abs", `Item #` %in% accuracy_all_two.three) %>% group_by(political_leaning, Par_Combined) %>%
  summarise(mean = mean(value), SD = sd(value), count = n(), se = (SD/(sqrt(count))), median = median(value), min = min(value), max = max(value))
accuracy_all_two.three

#making table
accuracy_all_two.three_table <- accuracy_all_two.three[1:2,-1]

accuracy_all_two.three %>%
  ggplot(aes(x = Par_Combined, y = mean, fill = as.factor(political_leaning))) + 
  geom_bar(stat = 'identity', position = 'dodge') + geom_errorbar(aes(ymin = mean-se, ymax =mean + se), width = .2, position = position_dodge(.9)) + theme_apa(legend.use.title = TRUE) + labs(title ="Accuracy across Dem and Rep favoured items", x = "Item Political Leaning", y = "Percent Accuracy", fill = "Pps Political Leaning") + scale_fill_manual(values=c("#0021F5", "#EA3223"))
```

## all items, familiarity thershold < 2.2 (political_true only)
```{r picking items on the basis of different levels of familarity 2.2 - true only}
# limited to 2.2
c_df_political_true %>% filter(measurement == "Fam", value < 2.2) %>%
  ggplot() + geom_bar(aes(x = `Image Name`, y = value, fill = Par_Combined), stat = 'identity', position = 'dodge') + theme_apa(legend.use.title = TRUE) + theme(axis.text.x = element_text(angle = 45, hjust = 1, size = 6)) + labs(title = "All items, familiarity < 2.2", x = "Image Name", y = "Familiarity", fill = "Item Pol. Leaning") + scale_fill_manual(values=c("#0021F5", "#EA3223"))

# need to find item numbers of those with Fam < 2.2 (across both dem and rep averaged)
# collapse across dem and rep - find average fam score, then exclude those that you don't need - make index from that.
accuracy_all_two.two <- c_df_political_true %>% group_by(`Item #`, `Image Name`, Par_Combined) %>% filter(measurement == "Fam") %>% summarise(mean = mean(value), SD = sd(value), count = n(), se = (SD/(sqrt(count))), median = median(value), min = min(value), max = max(value))

accuracy_all_two.two <- accuracy_all_two.two %>% filter(mean < 2.2)
accuracy_all_two.two <- accuracy_all_two.two[[1]]
# accuracy_all_two.two
# length(accuracy_all_two.two)

#given the index, now subset based on the index numbers.
accuracy_all_two.two <- c_df_political_true %>% filter(measurement == "Acc_Abs", `Item #` %in% accuracy_all_two.two) %>% group_by(political_leaning, Par_Combined) %>%
  summarise(mean = mean(value), SD = sd(value), count = n(), se = (SD/(sqrt(count))), median = median(value), min = min(value), max = max(value))
accuracy_all_two.two

#making table
accuracy_all_two.two_table <- accuracy_all_two.two[1:2,-1]

accuracy_all_two.two %>%
  ggplot(aes(x = Par_Combined, y = mean, fill = as.factor(political_leaning))) + 
  geom_bar(stat = 'identity', position = 'dodge') + geom_errorbar(aes(ymin = mean-se, ymax =mean + se), width = .2, position = position_dodge(.9)) + theme_apa(legend.use.title = TRUE) + labs(title ="Accuracy across Dem and Rep favoured items", x = "Item Political Leaning", y = "Percent Accuracy", fill = "Pps Political Leaning") + scale_fill_manual(values=c("#0021F5", "#EA3223"))

```

# Item selection (politically false only)
## all items, no familiarity thershold (political_false only)
```{r picking items on the basis of different levels of familarity - false only}
#all familiarity
c_df_political_false %>% filter(measurement == "Fam") %>%
  ggplot() + geom_bar(aes(x = `Image Name`, y = value, fill = Par_Combined), stat = 'identity', position = 'dodge') + theme_apa(legend.use.title = TRUE) + theme(axis.text.x = element_text(angle = 45, hjust = 1, size = 4)) + labs(title = "All items, all familiarity", x = "Image Name", y = "Familiarity", fill = "Item Pol. Leaning") + scale_fill_manual(values=c("#0021F5", "#EA3223"))


accuracy_all_fam <- c_df_political_false %>% filter(measurement == "Acc_Abs") %>% group_by(political_leaning, Par_Combined) %>% summarise(mean = mean(value), SD = sd(value), count = n(), se = (SD/(sqrt(count))), median = median(value), min = min(value), max = max(value))
accuracy_all_fam

accuracy_all_fam %>%
  ggplot(aes(x = Par_Combined, y = mean, fill = as.factor(political_leaning))) + 
  geom_bar(stat = 'identity', position = 'dodge') + geom_errorbar(aes(ymin = mean-se, ymax =mean + se), width = .2, position = position_dodge(.9)) + theme_apa(legend.use.title = TRUE) + labs(title ="Accuracy across Dem and Rep favoured items", x = "Item Political Leaning", y = "Percent Accuracy", fill = "Pps Political Leaning") + scale_fill_manual(values=c("#0021F5", "#EA3223"))


```

## all items, familiarity thershold < 3  (political_false only)
```{r picking items on the basis of different levels of familarity 3 - false only}
# limited to three
c_df_political_false %>% filter(measurement == "Fam", value < 3) %>%
  ggplot() + geom_bar(aes(x = `Image Name`, y = value, fill = Par_Combined), stat = 'identity', position = 'dodge') + theme_apa(legend.use.title = TRUE) + theme(axis.text.x = element_text(angle = 45, hjust = 1, size = 4)) + labs(title = "All items, familiarity < 3", x = "Image Name", y = "Familiarity", fill = "Item Pol. Leaning") + scale_fill_manual(values=c("#0021F5", "#EA3223"))

# need to find item numbers of those with Fam < 3 (across both dem and rep averaged)
# collapse across dem and rep - find average fam score, then exclude those that you don't need - make index from that.
accuracy_all_three_index <- c_df_political_false %>% group_by(`Item #`, `Image Name`, Par_Combined) %>% filter(measurement == "Fam") %>% summarise(mean = mean(value), SD = sd(value), count = n(), se = (SD/(sqrt(count))), median = median(value), min = min(value), max = max(value))

accuracy_all_three_index <- accuracy_all_three_index %>% filter(mean < 3)
accuracy_all_three_index <- accuracy_all_three_index[[1]]
# accuracy_all_three_index
# length(accuracy_all_three_index)

#given the index, now subset based on the index numbers.
accuracy_all_three <- c_df_political_false %>% filter(measurement == "Acc_Abs", `Item #` %in% accuracy_all_three_index) %>% group_by(political_leaning, Par_Combined) %>%
  summarise(mean = mean(value), SD = sd(value), count = n(), se = (SD/(sqrt(count))), median = median(value), min = min(value), max = max(value))
accuracy_all_three

#making table
accuracy_all_three_table <- rbind(accuracy_all_three_table, accuracy_all_three[1:2,-1])
accuracy_all_three_table$true_false <- c("Political_True", "Political_True", "Political_False", "Political_False")

accuracy_all_three %>%
  ggplot(aes(x = Par_Combined, y = mean, fill = as.factor(political_leaning))) + 
  geom_bar(stat = 'identity', position = 'dodge') + geom_errorbar(aes(ymin = mean-se, ymax =mean + se), width = .2, position = position_dodge(.9)) + theme_apa(legend.use.title = TRUE) + labs(title ="Accuracy across Dem and Rep favoured items", x = "Item Political Leaning", y = "Percent Accuracy", fill = "Pps Political Leaning") + scale_fill_manual(values=c("#0021F5", "#EA3223"))

```

## all items,  familiarity thershold < 2.5  (political_false only)
```{r picking items on the basis of different levels of familarity 2.5 - false only}
# limited to 2.5
c_df_political_false %>% filter(measurement == "Fam", value < 2.5) %>%
  ggplot() + geom_bar(aes(x = `Image Name`, y = value, fill = Par_Combined), stat = 'identity', position = 'dodge') + theme_apa(legend.use.title = TRUE) + theme(axis.text.x = element_text(angle = 45, hjust = 1, size = 5)) + labs(title = "All items, familiarity < 2.5", x = "Image Name", y = "Familiarity", fill = "Item Pol. Leaning") + scale_fill_manual(values=c("#0021F5", "#EA3223"))

# need to find item numbers of those with Fam < 2.5 (across both dem and rep averaged)
# collapse across dem and rep - find average fam score, then exclude those that you don't need - make index from that.
accuracy_all_two.five <- c_df_political_false %>% group_by(`Item #`, `Image Name`, Par_Combined) %>% filter(measurement == "Fam") %>% summarise(mean = mean(value), SD = sd(value), count = n(), se = (SD/(sqrt(count))), median = median(value), min = min(value), max = max(value))

accuracy_all_two.five <- accuracy_all_two.five %>% filter(mean < 2.5)
accuracy_all_two.five <- accuracy_all_two.five[[1]]
# accuracy_all_two.five
# length(accuracy_all_two.five)

#given the index, now subset based on the index numbers.
accuracy_all_two.five <- c_df_political_false %>% filter(measurement == "Acc_Abs", `Item #` %in% accuracy_all_two.five) %>% group_by(political_leaning, Par_Combined) %>%
  summarise(mean = mean(value), SD = sd(value), count = n(), se = (SD/(sqrt(count))), median = median(value), min = min(value), max = max(value))
accuracy_all_two.five

#making table
accuracy_all_two.five_table <- rbind(accuracy_all_two.five_table, accuracy_all_two.five[1:2,-1])
accuracy_all_two.five_table$true_false <- c("Political_True", "Political_True", "Political_False", "Political_False")

accuracy_all_two.five %>%
  ggplot(aes(x = Par_Combined, y = mean, fill = as.factor(political_leaning))) + 
  geom_bar(stat = 'identity', position = 'dodge') + geom_errorbar(aes(ymin = mean-se, ymax =mean + se), width = .2, position = position_dodge(.9)) + theme_apa(legend.use.title = TRUE) + labs(title ="Accuracy across Dem and Rep favoured items", x = "Item Political Leaning", y = "Percent Accuracy", fill = "Pps Political Leaning") + scale_fill_manual(values=c("#0021F5", "#EA3223"))

```

## all items, familiarity thershold < 2.4 (political_false only)
```{r picking items on the basis of different levels of familarity 2.4 - false only}
# limited to 2.4
c_df_political_false %>% filter(measurement == "Fam" , value < 2.4) %>%
  ggplot() + geom_bar(aes(x = `Image Name`, y = value, fill = Par_Combined), stat = 'identity', position = 'dodge') + theme_apa(legend.use.title = TRUE) + theme(axis.text.x = element_text(angle = 45, hjust = 1, size = 5)) + labs(title = "All items, familiarity < 2.4", x = "Image Name", y = "Familiarity", fill = "Item Pol. Leaning") + scale_fill_manual(values=c("#0021F5", "#EA3223"))

# need to find item numbers of those with Fam < 2.4 (across both dem and rep averaged)
# collapse across dem and rep - find average fam score, then exclude those that you don't need - make index from that.
accuracy_all_two.four <- c_df_political_false %>% group_by(`Item #`, `Image Name`, Par_Combined) %>% filter(measurement == "Fam") %>% summarise(mean = mean(value), SD = sd(value), count = n(), se = (SD/(sqrt(count))), median = median(value), min = min(value), max = max(value))

accuracy_all_two.four <- accuracy_all_two.four %>% filter(mean < 2.4)
accuracy_all_two.four <- accuracy_all_two.four[[1]]
# accuracy_all_two.four
# length(accuracy_all_two.four)

#given the index, now subset based on the index numbers.
accuracy_all_two.four <- c_df_political_false %>% filter(measurement == "Acc_Abs", `Item #` %in% accuracy_all_two.four) %>% group_by(political_leaning, Par_Combined) %>%
  summarise(mean = mean(value), SD = sd(value), count = n(), se = (SD/(sqrt(count))), median = median(value), min = min(value), max = max(value))
accuracy_all_two.four

#making table
accuracy_all_two.four_table <- rbind(accuracy_all_two.four_table, accuracy_all_two.four[1:2,-1])
accuracy_all_two.four_table$true_false <- c("Political_True", "Political_True", "Political_False", "Political_False")

accuracy_all_two.four %>%
  ggplot(aes(x = Par_Combined, y = mean, fill = as.factor(political_leaning))) + 
  geom_bar(stat = 'identity', position = 'dodge') + geom_errorbar(aes(ymin = mean-se, ymax =mean + se), width = .2, position = position_dodge(.9)) + theme_apa(legend.use.title = TRUE) + labs(title ="Accuracy across Dem and Rep favoured items", x = "Item Political Leaning", y = "Percent Accuracy", fill = "Pps Political Leaning") + scale_fill_manual(values=c("#0021F5", "#EA3223"))
```

## all items, familiarity thershold < 2.3 (political_false only)
```{r picking items on the basis of different levels of familarity 2.3 - false only}
# limited to 2.3
c_df_political_false %>% filter(measurement == "Fam", value < 2.3) %>%
  ggplot() + geom_bar(aes(x = `Image Name`, y = value, fill = Par_Combined), stat = 'identity', position = 'dodge') + theme_apa(legend.use.title = TRUE) + theme(axis.text.x = element_text(angle = 45, hjust = 1, size = 6)) + labs(title = "All items, familiarity < 2.3", x = "Image Name", y = "Familiarity", fill = "Item Pol. Leaning") + scale_fill_manual(values=c("#0021F5", "#EA3223"))

# need to find item numbers of those with Fam < 2.3 (across both dem and rep averaged)
# collapse across dem and rep - find average fam score, then exclude those that you don't need - make index from that.
accuracy_all_two.three <- c_df_political_false %>% group_by(`Item #`, `Image Name`, Par_Combined) %>% filter(measurement == "Fam") %>% summarise(mean = mean(value), SD = sd(value), count = n(), se = (SD/(sqrt(count))), median = median(value), min = min(value), max = max(value))

accuracy_all_two.three <- accuracy_all_two.three %>% filter(mean < 2.3)
accuracy_all_two.three <- accuracy_all_two.three[[1]]
# accuracy_all_two.three
# length(accuracy_all_two.three)

#given the index, now subset based on the index numbers.
accuracy_all_two.three <- c_df_political_false %>% filter(measurement == "Acc_Abs", `Item #` %in% accuracy_all_two.three) %>% group_by(political_leaning, Par_Combined) %>%
  summarise(mean = mean(value), SD = sd(value), count = n(), se = (SD/(sqrt(count))), median = median(value), min = min(value), max = max(value))
accuracy_all_two.three

#making table
accuracy_all_two.three_table <- rbind(accuracy_all_two.three_table, accuracy_all_two.three[1:2,-1])
accuracy_all_two.three_table$true_false <- c("Political_True", "Political_True", "Political_False", "Political_False")

accuracy_all_two.three %>%
  ggplot(aes(x = Par_Combined, y = mean, fill = as.factor(political_leaning))) + 
  geom_bar(stat = 'identity', position = 'dodge') + geom_errorbar(aes(ymin = mean-se, ymax =mean + se), width = .2, position = position_dodge(.9)) + theme_apa(legend.use.title = TRUE) + labs(title ="Accuracy across Dem and Rep favoured items", x = "Item Political Leaning", y = "Percent Accuracy", fill = "Pps Political Leaning") + scale_fill_manual(values=c("#0021F5", "#EA3223"))
```

## all items, familiarity thershold < 2.2 (political_false only)
```{r picking items on the basis of different levels of familarity 2.2 - false only}
# limited to 2.2
c_df_political_false %>% filter(measurement == "Fam", value < 2.2) %>%
  ggplot() + geom_bar(aes(x = `Image Name`, y = value, fill = Par_Combined), stat = 'identity', position = 'dodge') + theme_apa(legend.use.title = TRUE) + theme(axis.text.x = element_text(angle = 45, hjust = 1, size = 6)) + labs(title = "All items, familiarity < 2.2", x = "Image Name", y = "Familiarity", fill = "Item Pol. Leaning") + scale_fill_manual(values=c("#0021F5", "#EA3223"))

# need to find item numbers of those with Fam < 2.2 (across both dem and rep averaged)
# collapse across dem and rep - find average fam score, then exclude those that you don't need - make index from that.
accuracy_all_two.two <- c_df_political_false %>% group_by(`Item #`, `Image Name`, Par_Combined) %>% filter(measurement == "Fam") %>% summarise(mean = mean(value), SD = sd(value), count = n(), se = (SD/(sqrt(count))), median = median(value), min = min(value), max = max(value))

accuracy_all_two.two <- accuracy_all_two.two %>% filter(mean < 2.2)
accuracy_all_two.two <- accuracy_all_two.two[[1]]
# accuracy_all_two.two
# length(accuracy_all_two.two)

#given the index, now subset based on the index numbers.
accuracy_all_two.two <- c_df_political_false %>% filter(measurement == "Acc_Abs", `Item #` %in% accuracy_all_two.two) %>% group_by(political_leaning, Par_Combined) %>%
  summarise(mean = mean(value), SD = sd(value), count = n(), se = (SD/(sqrt(count))), median = median(value), min = min(value), max = max(value))
accuracy_all_two.two

#making table
accuracy_all_two.two_table <- rbind(accuracy_all_two.two_table, accuracy_all_two.two[1:2,-1])
accuracy_all_two.two_table$true_false <- c("Political_True", "Political_True", "Political_False", "Political_False")

accuracy_all_two.two %>%
  ggplot(aes(x = Par_Combined, y = mean, fill = as.factor(political_leaning))) + 
  geom_bar(stat = 'identity', position = 'dodge') + geom_errorbar(aes(ymin = mean-se, ymax =mean + se), width = .2, position = position_dodge(.9)) + theme_apa(legend.use.title = TRUE) + labs(title ="Accuracy across Dem and Rep favoured items", x = "Item Political Leaning", y = "Percent Accuracy", fill = "Pps Political Leaning") + scale_fill_manual(values=c("#0021F5", "#EA3223"))

```

# Tables of familiarity across True and False items
```{r item selection tables}
#fam < 3
accuracy_all_three_table
# accuracy_all_three_table$true_false <- factor(accuracy_all_three_table$true_false, levels = c("Political_True", "Political_False"))

# accuracy_all_three_table %>% ggplot() + geom_bar(aes(x = Par_Combined, y = count, fill = Par_Combined), stat = 'identity', position = 'dodge') + theme_apa(legend.use.title = TRUE) + labs(title = "Item Count, fam < 3", x = "Item Pol. Leaning", y = "Count", fill = "Item Pol. Leaning") + facet_wrap(~true_false) + scale_fill_manual(values=c("#0021F5", "#EA3223"))

#fam < 2.5
accuracy_all_two.five_table

#fam < 2.4
accuracy_all_two.four_table

#fam < 2.3
accuracy_all_two.three_table

#fam < 2.2
accuracy_all_two.two_table

```

```{r}
#  final selection
# View(c_df_political_true %>% filter(measurement == "Fam", Par_Combined == "Dem Favoured", political_leaning == "Democrat"))

tmp <- c_df_political_true %>% filter(measurement == "Fam", Par_Combined == "Dem Favoured", political_leaning == "Democrat")

tmp <- rbind(tmp, c_df_political_true %>% filter(measurement == "Fam", Par_Combined == "Rep Favoured", political_leaning == "Democrat"))

tmp <- rbind(tmp, c_df_political_false %>% filter(measurement == "Fam", Par_Combined == "Dem Favoured", political_leaning == "Democrat"))

tmp <- rbind(tmp, c_df_political_false %>% filter(measurement == "Fam", Par_Combined == "Rep Favoured", political_leaning == "Democrat"))

write_xlsx(
  tmp,
  path = "item_selection - review.xlsx",
  col_names = TRUE)
```

# Partisian 
```{r preparing df to run histograms for political leaning}

# removing unnecessary columns
df_slim_leaning <- df[, c("Item #", "Category", "Image Name", "Headline Summary", "Par_Dem", "Par_Rep", "Par_Combined")]

#add whether the items are democratic favoured or republican favoured
df_slim_leaning$Par_Combined_Categ <- ifelse(df_slim_leaning$Par_Combined > 3.5, "Rep Favoured", "Dem Favoured")

# long format
df_slim_leaning_long <- gather(df_slim_leaning, key = "measurement", value = "value", -c("Item #", "Category", "Image Name", "Headline Summary", "Par_Combined_Categ"))

# adding political variable
df_slim_leaning_long$political_leaning <- "Democrat"

df_slim_leaning_long$political_leaning <- ifelse(str_detect(df_slim_leaning_long$measurement, "Rep") == TRUE, df_slim_leaning_long$political_leaning <- "Republican", df_slim_leaning_long$political_leaning <- "Democrat")

df_slim_leaning_long$political_leaning[str_detect(df_slim_leaning_long$measurement, "Combined")] <- "Combined"
df_slim_leaning_long$Par_Combined_Categ[str_detect(df_slim_leaning_long$measurement, "Combined")] <- "Combined"

df_slim_leaning_long$measurement <- str_replace(df_slim_leaning_long$measurement, c("_Rep"), "")
df_slim_leaning_long$measurement <- str_replace(df_slim_leaning_long$measurement, c("_Dem"), "")
df_slim_leaning_long$measurement <- str_replace(df_slim_leaning_long$measurement, c("_Combined"), "")

#adding classesf
df_slim_leaning_long$Par_Combined_Categ <- factor(df_slim_leaning_long$Par_Combined_Categ, levels = c("Dem Favoured", "Rep Favoured", "Combined"))

df_slim_leaning_long <- df_slim_leaning_long %>% filter(Category == "Political_True" | Category == "Political_Fake")

# removing those high or low in accuracy 
# after identifying which items to remove now creating new corrected dfs
df_slim_leaning_long <- df_slim_leaning_long %>% filter(`Item #` %notin% index_remove_all)

```

```{r histograms partisanship}

df_slim_leaning_long %>% group_by(Category, political_leaning) %>%
  summarise(mean = mean(value), SD = sd(value), count = n(), se = (SD/(sqrt(count))), median = median(value), min = min(value), max = max(value))

# Basic histogram partisanship combined
df_slim_leaning_long %>% filter(political_leaning == "Combined") %>% ggplot(aes(x=value)) + geom_histogram() + theme_apa() + labs(title = "Partisanship - Combined", x = "Likert Values", y = "Count",  subtitle = "If accurate, how favorable to Democrats vs. Republicans (>= 4: Rep)") + geom_vline(aes(xintercept = mean(value)), linetype="dashed") + ylim(0,12.5)

# Basic histogram partisanship combined facet
df_slim_leaning_long %>% filter(political_leaning == "Combined") %>% ggplot(aes(x=value)) + geom_histogram() + theme_apa() + labs(title = "Partisanship - Combined", x = "Likert Values", y = "Count",  subtitle = "If accurate, how favorable to Democrats vs. Republicans (>= 4: Rep)") + facet_wrap(~Category) + ylim(0,12.5)

# Basic histogram partisanship dems only
df_slim_leaning_long %>% filter(political_leaning == "Democrat") %>% ggplot(aes(x=value)) + geom_histogram() + theme_apa() + labs(title = "Partisanship - Democrats Only", x = "Likert Values", y = "Count",  subtitle = "If accurate, how favorable to Democrats vs. Republicans (>= 4: Rep)") + geom_vline(aes(xintercept = mean(value)), linetype="dashed") + ylim(0,12.5)

# Basic histogram partisanship dems only facet
df_slim_leaning_long %>% filter(political_leaning == "Democrat") %>% ggplot(aes(x=value)) + geom_histogram() + theme_apa() + labs(title = "Partisanship - Democrats Only", x = "Likert Values", y = "Count",  subtitle = "If accurate, how favorable to Democrats vs. Republicans (>= 4: Rep)") + facet_wrap(~Category) + ylim(0,12.5)

# Basic histogram partisanship reps
df_slim_leaning_long %>% filter(political_leaning == "Republican") %>% ggplot(aes(x=value)) + geom_histogram() + theme_apa() + labs(title = "Partisanship - Republicans Only", x = "Likert Values", y = "Count",  subtitle = "If accurate, how favorable to Democrats vs. Republicans (>= 4: Rep)") + geom_vline(aes(xintercept = mean(value)), linetype="dashed") + ylim(0,12.5)

# Basic histogram partisanship reps facet
df_slim_leaning_long %>% filter(political_leaning == "Republican") %>% ggplot(aes(x=value)) + geom_histogram() + theme_apa() + labs(title = "Partisanship - Republicans Only", x = "Likert Values", y = "Count",  subtitle = "If accurate, how favorable to Democrats vs. Republicans (>= 4: Rep)") + facet_wrap(~Category) + ylim(0,12.5)

# Basic histogram all partisanship factors
df_slim_leaning_long %>% ggplot(aes(x=value)) + geom_histogram() + theme_apa() + labs(title = "Partisanship - All factors", x = "Likert Values", y = "Count",  subtitle = "If accurate, how favorable to Democrats vs. Republicans (>= 4: Rep)") + facet_wrap(~political_leaning)

```

